### 2023-06-18 Draft.tex
Added code for borders

@@

An interesting note is that, when the kernel is convolved with an impulse signal(an image with 0 everywhere except the origin),
it reproduces the kernel itself, whereas with correlational filtering, it produces the reflected signal.
$$
\underbrace{
    \begin{bmatrix}
        128 & 34 & 123\\
        68 & 54 & 73 \\
        100 & 95 & 17
    \end{bmatrix}}_{\text{input neighborhood}}
\otimes
\underbrace{
    \begin{bmatrix}
        0.1 & 0.1 & 0.1\\
        0.1 & 0.2 & 0.1\\
        0.1 & 0.1 & 0.1
    \end{bmatrix}}_{\text{kernel}}
= 75
$$

@@

Another common variant on the formula is having the signs of the offsets reversed.
\[
    g = f \ast h
\]
\[
    g(i,j) = \sum_{l \in \mathscr{M}}\sum_{k \in \mathscr{N}}{f(i-k, j-l) \cdot h(k, l)}
\]
With this formula, $\ast$ is called the \emph{convolutional} operator, and the kernel $h$ is called the \emph{impulse response function}.

% TEMPLATE EXAMPLES BELOW
\newpage
\section{example page from template}
Please specify your name, matriculation number, the name of your advisor and the title of your report in 
\verb+titlepage.tex+.

@@

Similarly to tables, we can also create figures. Fig.~\ref{fig:example_figure} also got a number.

@@

Equations are numbered as well, \eg, above we have Eq.~\ref{eq:someformula}.

% =========================================================================
\bibliographystyle{alpha}
\bibliography{abbrev,seminar_report}
\end{document}

>>>>

\usepackage{float} %figure inside minipage

@@

$$
\underbrace{
    \begin{bmatrix}
        128 & 34 & 123\\
        68 & 54 & 73 \\
        100 & 95 & 17
    \end{bmatrix}}_{\text{input neighborhood}}
\otimes
\underbrace{
    \begin{bmatrix}
        0.1 & 0.1 & 0.1\\
        0.1 & 0.2 & 0.1\\
        0.1 & 0.1 & 0.1
    \end{bmatrix}}_{\text{kernel}}
= 75
$$

@@

Another common variant on the formula is having the signs of the offsets reversed. 
\[
    g = f \ast h
\]
\[
    g(i,j) = \sum_{l \in \mathscr{M}}\sum_{k \in \mathscr{N}}{f(i-k, j-l) \cdot h(k, l)}
\]
With this formula, $\ast$ is called the \emph{convolutional} operator, and the kernel $h$ is called the \emph{impulse response function}. An interesting note is that, 
when the kernel $h$ is convolved with an impulse signal $\delta$ (an image with 0 everywhere except the origin),
it reproduces the kernel itself $h \ast \delta = h$, whereas with correlational filtering, it produces the reflected signal (inverted signal in both dimensions).\\

An apparent problem from neighborhood filtering is that on the edges, the neighbors simply does not exist in one or two directions (e.g. a $1000\times1000$ image passed
through a $3\times3$ kernel would produce a $998\times998$ image). There are a couple method to alleviate the calculation of the nonexistent neighbors.

\begin{minipage}{\textwidth}\begin{figure}[H]
    \centering
    \subfigure[zero]{\includegraphics[width=0.24\textwidth]{img/border_constant}}
    \subfigure[wrap]{\includegraphics[width=0.24\textwidth]{img/border_wrap}}
    \subfigure[clamp]{\includegraphics[width=0.24\textwidth]{img/border_clamp}}
    \subfigure[mirror]{\includegraphics[width=0.24\textwidth]{img/border_reflect}}

\end{figure}\end{minipage}

% TEMPLATE EXAMPLES BELOW===========================================
\newpage
\section{example page from template}
Please specify your name, matriculation number, the name of your advisor and the title of your report in 
\verb+titlepage.tex+.

@@

% Similarly to tables, we can also create figures. Fig.~\ref{fig:example_figure} also got a number.

@@

Equations are numbered as well, \eg, above we have Eq.~\ref{eq:someformula}.\cite{Kingma14Arxiv}

% =========================================================================
\bibliographystyle{alpha}
\bibliography{abbrev,Draft}
\end{document}
